Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
Checked Organization inputs and persona inputs

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     'Always'))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c('TV',
                     'Print',
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

@@

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

@@

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

@@

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

@@

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly Agree"))

@@

selectInput("p3_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

@@

textInput("gp_id",
          label = "Organization Name",
          value = "Organization 2",
          placeholder = "Enter Organiation Name"
)

@@

textInput("ox_id",
          label = "Organization Name",
          value = "Organization 3",
          placeholder = "Enter Organiation Name"
)

@@

textInput("rc_id",
          label = "Organization Name",
          value = "Organization 4",
          placeholder = "Enter Organiation Name"
)

>>>>

selectInput("p1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"))

selectInput("p1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE)

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

@@

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

@@

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

@@

selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

@@

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"))

@@

selectInput("p3_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

@@

textInput("gp_id",
          label = "Organization Name",
          value = "Organization 2",
          placeholder = "Enter Organiation Name")

@@

textInput("ox_id",
          label = "Organization Name",
          value = "Organization 3",
          placeholder = "Enter Organiation Name")

@@

textInput("rc_id",
          label = "Organization Name",
          value = "Organization 4",
          placeholder = "Enter Organiation Name")
